### 2017-10-13 Gruba/02-overview.tex

\begin{definition}
\label{def:user}
Given a user $u$, $B_u$, $R_u$ and $E_u$ represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee per se refers to a user.
\end{definition}

>>>>

\begin{definition}
\label{def:user}
Given a user $u$, we adopt $B_u$, $R_u$ and $E_u$ to represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee per se refers to a user.
\end{definition}
